Supplementary information

### 2021-01-04 manuscript/supplementary_figures.Rmd
box plots added to categorical descriptor supplementary figures

```{r PDIfactor,fig.height=8,fig.cap='Categorical descriptors plotted against the PDI.'}
descriptor_scatter_plots$PDI_factor
```

@@

```{r DAIfactor,fig.height=8,fig.cap='Categorical descriptors plotted against the DAI.'}
descriptor_scatter_plots$DAI_factor
```

>>>>

```{r PDIfactor,fig.height=9,fig.cap='PDI box plots of the categorical descriptors.'}
descriptor_scatter_plots$PDI_factor
```

@@

```{r DAIfactor,fig.height=9,fig.cap='DAI box plots of the categorical descriptors.'}
descriptor_scatter_plots$DAI_factor
```
